Contextual recruitment of selective attention can be updated via changes in task-relevance

### 2019-08-07 manuscript_pretty.Rmd
revision in progress

Memory-based perspectives however, take a more nuanced view [@norman_memory_1969; @norman_memory_1976; @abrahamse_grounding_2016; @brosowsky_memory-guided_2018; @crump_learning_2016; @egner_creatures_2014]. Here, practice is only important to the extent that it improves memory retrieval. If a few prior experiences are distinct, and easily retrievable, it could support the reinstatement of a learned attentional association despite very little practice [e.g., @brosowsky_memory-guided_2018]. Conversely, if prior experiences are difficult to retrieve, then learned associations may not be expressed, even after much practice. This view offers one potential path for flexibility in the expression of learned associations. Learning an association is the process of encoding into memory experiences where attentional priorities and cues co-occur. Memory retrieval is a similarity-based, cue-driven process [e.g., @jacoby_interpreting_1978; @hintzman_minerva_1984; @hintzman_schema_1986; @hintzman_judgments_1988]. Presumably, the features of our immediate environment automatically cue memory and reinstate the retrieved attentional priorites [@logan_toward_1988; @logan_attention_1992]. However, to the extent that you could manipulate memory retrieval, you should be able manipulate the expression of learned associations.

@@

Previous work has shown that shifting between list-wide proportion congruent phases produced asymmetrical effects. Specifically, @abrahamse_attention_2013 found that shifting from a mostly-congruent to mostly-incongruent list produced a large change in the size of the congruency effect, whereas shifting from a mostly-incongruent to mostly-congruent list produced a relatively small change in congruency effects. The authors suggested that the assymetry is caused by a learned attentional modulation in the mostly-incongruent block carrying over into the mostly-congruent block. In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from the use of one context cue to another. We therefore randomized the order across participants to control for the effects of order. However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was asymmetrical.

>>>>

Memory-based perspectives however, take a more nuanced view [@norman_memory_1969; @norman_memory_1976; @abrahamse_grounding_2016; @brosowsky_memory-guided_2018; @crump_learning_2016; @egner_creatures_2014]. Here, practice is only important to the extent that it improves memory retrieval. Learning an association is the process of encoding experiences, where attentional priorities and cues co-occur, into memory. Memory retrieval is a similarity-based, cue-driven process [e.g., @jacoby_interpreting_1978; @hintzman_minerva_1984; @hintzman_schema_1986; @hintzman_judgments_1988]. Presumably, the features of our immediate environment automatically cue memory and reinstate the retrieved attentional priorites [@logan_toward_1988; @logan_attention_1992]. If a few prior experiences are easily retrievable--memories are distinct or very similar to the retrieval cue--it could support the reinstatement of a learned attentional association despite very little practice [e.g., @brosowsky_memory-guided_2018]. Conversely, if prior experiences are difficult to retrieve--memories are in or low in similarity to the retrieval cue--then learned associations may not be expressed, even after much practice. To the extent that you could manipulate memory retrieval, you should be able manipulate the expression of learned associations.

@@

Previous work has shown that shifting between list-wide proportion congruent phases produced asymmetrical effects. Specifically, @abrahamse_attention_2013 found that shifting from a mostly-congruent to mostly-incongruent list produced a large change in the size of the congruency effect, whereas shifting from a mostly-incongruent to mostly-congruent list produced a relatively small change in congruency effects. The authors posited a learned attentional modulation in the mostly-incongruent block had carried over into the mostly-congruent block. In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from the use of one context cue to another. We therefore randomized the order across participants to control for the effects of order. However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was asymmetrical.
